### 2023-03-14 README.Rmd
prepare for cran

[![CRAN status](https://www.r-pkg.org/badges/version/pema)](https://CRAN.R-project.org/package=pema)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://r-pkg.org/pkg/pema)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions)
<!-- [![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions) -->
<!-- [![codecov](https://codecov.io/gh/cjvanlissa/pema/branch/master/graph/badge.svg?token=7S9XKDRT4M)](https://codecov.io/gh/cjvanlissa/pema) -->
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-v2.0%20adopted-ff69b4.svg)](https://www.contributor-covenant.org/version/2/0/code_of_conduct.html)
<!-- [![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969) -->

>>>>

[![CRAN status](https://www.r-pkg.org/badges/version/pema)](https://CRAN.R-project.org/package=pema)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://cran.rstudio.com/web/packages/pema/index.html)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions)
<!-- [![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions) -->
<!-- [![codecov](https://codecov.io/gh/cjvanlissa/pema/branch/master/graph/badge.svg?token=7S9XKDRT4M)](https://codecov.io/gh/cjvanlissa/pema) -->
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-v2.0%20adopted-ff69b4.svg)](https://www.contributor-covenant.org/version/2/0/code_of_conduct.html)
<!-- [![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969) -->
